Visit Scotland Notebook

### 2023-06-13 visit_scotland_notebook.Rmd
Drafted Basic Activities Plots / Cleaned Additional USA Visitor Data

demographics_all <- read_csv(here("data/clean_data/all_demographics_clean.csv"))
employment_demographics <- read_csv(here("data/clean_data/employment_demographics_clean.csv"))
gender_demographics <- read_csv(here("data/clean_data/gender_demographics_clean.csv"))
age_demographics <- read_csv(here("data/clean_data/age_demographics_clean.csv"))
marital_demographics <- read_csv(here("data/clean_data/marital_status_demographics_clean.csv"))
children_demographics <- read_csv(here("data/clean_data/children_demographics_clean.csv"))
car_demographics <- read_csv(here("data/clean_data/car_demographics_clean.csv"))
social_demographics <- read_csv(here("data/clean_data/social_demographics_clean.csv"))
regional_domestic_tourism <- read_csv(here("data/clean_data/regional_domestic_tourism_clean.csv"))
activities <- read_csv(here("data/clean_data/activities_clean.csv"))

@@

demographics_all %>% 
  ggplot(aes(x = year, y = expenditure, group = 1)) +
  geom_line(size = 1, colour = "grey") +
  geom_point(aes(colour = exp_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year",
       y = "Expenditure (Million) \n",
       title = "Expenditure Over Time") +
  scale_y_continuous(limits = c(0, 6500), breaks = c(0, 2000, 4000, 6000)) +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))

@@

demographics_all %>% 
  ggplot(aes(x = year, y = exp_per_visit, group = 1)) +
  geom_line(size = 1, colour = "grey") +
  geom_point(aes(colour = exp_per_visit_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year",
       y = "Expenditure (Millions) per Visit (Millions) \n",
       title = "Expenditure To Visit Ratio \n") +
  scale_y_continuous(limits = c(0, 60), breaks = c(0, 20, 40, 60)) +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))

@@

```{r}
age_demographics %>%
  group_by(age) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = reorder(age, mean_exp_per_visit), y = mean_exp_per_visit, fill = age == "45-54 years"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Age",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Age Group") +
  coord_flip()
```

@@

>>>>

demographics_all <- read_csv(here("data/clean_data/all_demographics_clean.csv"))
employment_demographics <- read_csv(here("data/clean_data/employment_demographics_clean.csv"))
gender_demographics <- read_csv(here("data/clean_data/gender_demographics_clean.csv"))
age_demographics <- read_csv(here("data/clean_data/age_demographics_clean.csv"))
marital_demographics <- read_csv(here("data/clean_data/marital_status_demographics_clean.csv"))
children_demographics <- read_csv(here("data/clean_data/children_demographics_clean.csv"))
car_demographics <- read_csv(here("data/clean_data/car_demographics_clean.csv"))
social_demographics <- read_csv(here("data/clean_data/social_demographics_clean.csv"))
regional_domestic_tourism <- read_csv(here("data/clean_data/regional_domestic_tourism_clean.csv"))
activities <- read_csv(here("data/clean_data/activities_clean.csv"))
usa_visit_spend_region <- read_csv(here("data/clean_data/usa_visit_spend_region_clean.csv"))

@@

demographics_all %>% 
  ggplot(aes(x = year, y = expenditure, group = 1)) +
  geom_line(size = 1, colour = "grey") +
  geom_point(aes(colour = exp_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year",
       y = "Expenditure (Million Pounds, GBP) \n",
       title = "Expenditure Over Time") +
  scale_y_continuous(limits = c(0, 6500), breaks = c(0, 2000, 4000, 6000)) +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))

@@

demographics_all %>% 
  ggplot(aes(x = year, y = exp_per_visit, group = 1)) +
  geom_line(size = 1, colour = "grey") +
  geom_point(aes(colour = exp_per_visit_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year",
       y = "Expenditure (Million Pounds, GBP) per Visit (Millions) \n",
       title = "Expenditure Per Visit \n") +
  scale_y_continuous(limits = c(0, 60), breaks = c(0, 20, 40, 60)) +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))

@@

```{r}
age_demographics %>%
  group_by(age) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = reorder(age, mean_exp_per_visit), y = mean_exp_per_visit, fill = age == "45-54 years"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Age",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019") +
  coord_flip()
```

@@

## Activities

```{r}
activities %>%
  group_by(tourism_activity) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = reorder(tourism_activity, mean_exp_per_visit), y = mean_exp_per_visit,
               fill = tourism_activity == "Shopping for Non-Regular Purchases"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Activity",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2013-2019") +
  coord_flip()
```

```{r}
activities %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(tourism_activity, is_2019) %>%
  arrange(tourism_activity) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = reorder(tourism_activity, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Activity",
    y = "% Difference \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018 Avg.") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format(scale = 1))
```
